% ss_story.tex

% Legend of the Shuffling Spires of Thin
\subsection{Legend of the Shuffling Spires of Thin}
\label{sec:legendoftheshufflingspiresofthin}
Old tales tell of the mystic Kingdoms of Thin, all of which border in four equally divided parts of a circle - in the Realm of Thin-Things.
These kingdoms were ruled by four power-hungry Kings, each jealous of the next, their fair Queens, brave Jacks and top $10$ Henchmen numbered - you guessed it - one through ten.
Even though the Kings’ respective wealth were great, they were not content with ruling only one of the Kingdoms of Thin. Each wanted to claim the entire Realm for their own. Since all Kingdoms were equally thin, this would require very precise plotting.
...and we all know that plotting means spying, and you cannot spell ‘spyglass’ without ‘spy’, and the only way to use a spyglass effectively is to use it from something very wide, lengthy or high.

Since width is hard to come by in the Realm of Thin-Things, and ‘length’ is a more bothersome word, the Kings all plotted to construct high Spires, so they could spy far-away from their Kingdom - for the right moment when they could claim the Realm for themselves.

The problem with spires, though, is that they’re immobile - and once you’ve placed a spire it may be hard to move it if one would wish to spy somewhere else.
After all, to dominate the Realm of Thin-Things, one would have to spy on all four Kingdoms!

Luckily, in the Lands of Thin, one may construct remarkably thin-things.
So the Kings plotted to build four equally high and thin spires, all constructed in three very - even in the Realm of Thin-Things - thin sections.
The low parts were assigned to the Jacks, who were the most suitable 'Thins' to guard and protect the towers, the middle bits were assigned to the Queens and the highest sections were given unto the Kings themselves.

These sections were so amazingly thin that the wind would easily carry them anywhere across the Lands of Thin. This way; the Kings could spy on all of their neighbours in wait for the right moment to strike.

When this opportunity had come it was decided that the Kingdoms’ ten best Henchmen were to launch an all-out assault targeted at the other Kingdoms.
This would be the way to a unified Realm of Thin-Things, thought the Kings.

And so one day a mighty storm swept the Kingdoms of Thin and took even the least-thin Henchmen aloft.
The Realm was veiled in powerful winds, the likes of which neither Kingdom had ever seen. In the midst of all this chaos, all four Kings decided to put their respective master plan to work and gaze from their high Spires as they conquered the Lands of Thin.

But it came to pass that the Kings of Thin were also men of thin intellect, as it did not occur to them that their high Spires had also been swept from the lands and were being taken far away from their Kingdom. The High Spires of Thin were swept across the Realm, across the Kingdoms of Thin and shuffled so that neither King knew what Kingdom nor Spire he was in.
Yet neither side's Henchmen saw any difference.

The Kings and their Shuffling Spires were about to be attacked by not only the other armies, but by their own.
Thus, the Legend of the Shuffling Spires of Thin was made.

\textbf{Shuffle-Spires} is based around the four Kings, and the Legendary Spires of Thin.